Who does big team science?

### 2023-03-10 manuscript_scopus.Rmd
adding new stuff

```{r setup, include = FALSE}
#knitr::opts_knit(echo = TRUE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
```

```{r data, include = FALSE}
geo_country <- import("py_outputs/geo_country.xlsx")
geo_region <- import("py_outputs/geo_region.xlsx")
```

@@

```{r geo-map}
# serbia has changed codes
geo_country$affiliation_tag_country <- toupper(geo_country$affiliation_tag_country)
geo_country <- subset(geo_country, affiliation_tag_country != "NONE")
geo_country$affiliation_tag_country[geo_country$affiliation_tag_country == "SCG"] <- "SRB"

geo_country <- geo_country %>% 
  group_by(affiliation_tag_country) %>% 
  summarize(count = sum(count))

@@

# make a map on a continuous scale
ggplot(geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  scale_fill_distiller(name = "Sample Size",
                       palette = "Greys",
                       direction = 1,
                       na.value = "white")

@@

# maybe try binning
geo_country$count_binned <- if_else(
  geo_country$count >= 10000, "10,000+", 
  if_else(
    geo_country$count < 10000 & geo_country$count >= 5000, "5,000-9,999",
    if_else(
      geo_country$count < 5000 & geo_country$count >= 1000, "1,000-4,999",
      if_else(
        geo_country$count < 1000 & geo_country$count >= 100, "100-999",
        "< 100"
      )
    )
  )
)

geo_country$count_binned <- factor(geo_country$count_binned, 
                                   levels = unique(geo_country$count_binned))

# map of binned data 
bin_country <- ggplot(geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  scale_fill_manual(name = "Sample Size",
                    values = c( "black", "#323232", "#646464","#969696","#c8c8c8"))

@@

# tree map
geo_country$un_region_sub <- countrycode(
  sourcevar = geo_country$affiliation_tag_country,
  origin = 'iso3c', 
  destination = 'un.regionsub.name'
)

geo_country$un_region <- countrycode(
  sourcevar = geo_country$affiliation_tag_country,
  origin = 'iso3c', 
  destination = 'un.region.name'
)

geo_country$un_region[geo_country$affiliation_tag_country == "TWN"] <- "Asia"
geo_country$un_region_sub[geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"

geo_country <- geo_country %>% 
  na.omit()

tree <- ggplot(geo_country, aes(area = count, fill = count_binned,
               label = affiliation_tag_country, subgroup = un_region_sub)) +
  geom_treemap() +
  geom_treemap_subgroup_border(colour = "white", size = 5) +
  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
  #                            alpha = 0.25, colour = "black",
  #                            fontface = "italic") +
  geom_treemap_text(colour = "white", place = "centre",
                    size = 15, grow = FALSE) +  
  scale_fill_manual(name = "Sample Size",
                    values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
  # scale_fill_gradient(name = "Sample Size",
  #                     low = "#c8c8c8", 
  #                     high = "#323232")

@@

@@

```{r}
library(tidyr)
geo_region_wide <- geo_region %>% 
  pivot_wider(id_cols = Year, 
              names_from = aff_un, 
              values_from = count,
              values_fill = 0)
```

>>>>

```{r setup, include = FALSE}
#knitr::opts_knit(echo = TRUE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
```

```{r data, include = FALSE}
# things to import
var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
              "medium_other_gp", "normal_pub_type", "pub_time_count", 
              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp")

var_list_import <- paste0("py_outputs/", var_list, ".xlsx")

DF <- lapply(var_list_import, import)
names(DF) <- var_list
```

@@

```{r geo-map}
# serbia has changed codes
DF$geo_country$affiliation_tag_country <- toupper(DF$geo_country$affiliation_tag_country)
DF$geo_country <- subset(DF$geo_country, affiliation_tag_country != "NONE")
DF$geo_country$affiliation_tag_country[DF$geo_country$affiliation_tag_country == "SCG"] <- "SRB"

DF$geo_country <- DF$geo_country %>% 
  group_by(affiliation_tag_country) %>% 
  summarize(count = sum(count))

@@

# make a map on a continuous scale
ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  scale_fill_distiller(name = "Sample Size",
                       palette = "Greys",
                       direction = 1,
                       na.value = "white")

@@

# maybe try binning
DF$geo_country$count_binned <- if_else(
  DF$geo_country$count >= 10000, "10,000+", 
  if_else(
    DF$geo_country$count < 10000 & DF$geo_country$count >= 5000, "5,000-9,999",
    if_else(
      DF$geo_country$count < 5000 & DF$geo_country$count >= 1000, "1,000-4,999",
      if_else(
        DF$geo_country$count < 1000 & DF$geo_country$count >= 100, "100-999",
        "< 100"
      )
    )
  )
)

DF$geo_country$count_binned <- factor(DF$geo_country$count_binned, 
                                   levels = unique(DF$geo_country$count_binned))

# map of binned data 
bin_country <- ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  scale_fill_manual(name = "Sample Size",
                    values = c( "black", "#323232", "#646464","#969696","#c8c8c8"))

@@

# tree map
DF$geo_country$un_region_sub <- countrycode(
  sourcevar = DF$geo_country$affiliation_tag_country,
  origin = 'iso3c', 
  destination = 'un.regionsub.name'
)

DF$geo_country$un_region <- countrycode(
  sourcevar = DF$geo_country$affiliation_tag_country,
  origin = 'iso3c', 
  destination = 'un.region.name'
)

DF$geo_country$un_region[DF$geo_country$affiliation_tag_country == "TWN"] <- "Asia"
DF$geo_country$un_region_sub[DF$geo_country$affiliation_tag_country == "TWN"] <- "Eastern Asia"

DF$geo_country <- DF$geo_country %>% 
  na.omit()

tree <- ggplot(DF$geo_country, aes(area = count, fill = count_binned,
               label = affiliation_tag_country, subgroup = un_region_sub)) +
  geom_treemap() +
  geom_treemap_subgroup_border(colour = "white", size = 5) +
  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
  #                            alpha = 0.25, colour = "black",
  #                            fontface = "italic") +
  geom_treemap_text(colour = "white", place = "centre",
                    size = 15, grow = FALSE) +  
  scale_fill_manual(name = "Sample Size",
                    values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
  # scale_fill_gradient(name = "Sample Size",
  #                     low = "#c8c8c8", 
  #                     high = "#323232")

@@

```{r}
label <- c("Physical", "Social", "Health", "Life")
b_values <- c(-0.061001, -0.077040, -0.017775, -0.014946)
se_values <- c(0.022958, 0.058153, 0.009794, 0.010485)
r2_values <- c(0.002357, 0.004491, 0.000434, 0.000434)
sample_size <- 13000

r2_low <- 1:length(r2_values)
r2_high <- 1:length(r2_values)
for (i in 1:length(r2_values)){
  temp <- ci.R2(R2 = r2_values[i], 1, sample_size)
  r2_low[i] <- temp$Lower.Conf.Limit.R2
  r2_high[i] <- temp$Upper.Conf.Limit.R2
}

graph_data <- data.frame(
  "label" = label,
  "estimate" = b_values,
  "type" = "Coefficient",
  "low" = b_values - qt(.025, sample_size, lower.tail = F)*se_values,
  "high" = b_values + qt(.025, sample_size, lower.tail = F)*se_values) %>% 
  bind_rows(
    data.frame(  
      "label" = label, 
      "estimate" = r2_values,
      "type" = "Effect Size",
      "low" = r2_low,
      "high" = r2_high)
  )

ggplot(graph_data, aes(label, estimate)) + 
  geom_point() +
  geom_pointrange(aes(ymin = low, ymax = high)) +
  theme_classic() + 
  facet_wrap(~type) + 
  geom_hline(yintercept = 0) + 
  coord_flip() + 
  xlab("Subject Area") + 
  ylab("")
```

@@

```{r}
DF$small_first_gp <- DF$small_first_gp %>% 
  pivot_wider(id_cols = Year, 
              names_from = aff_un, 
              values_from = count,
              values_fill = 0)

DF$small_other_gp <- DF$small_other_gp %>% 
  pivot_wider(id_cols = Year, 
              names_from = aff_un, 
              values_from = count,
              values_fill = 0) %>% 
  select(colnames(DF$small_first_gp))

small_effect <- data.frame(
  year = 1:length(unique(DF$small_first_gp$Year)),
  v = 1:length(unique(DF$small_first_gp$Year)),
  low = 1:length(unique(DF$small_first_gp$Year)),
  high = 1:length(unique(DF$small_first_gp$Year))
)
i <- 1
for (year in unique(DF$small_first_gp$Year)){
  temp_table <- DF$small_first_gp %>% filter(Year == year) %>% select(-Year) %>% 
    bind_rows(DF$small_other_gp %>% filter(Year == year) %>% select(-Year))

  col_total <- colSums(temp_table)
  temp_table <- temp_table %>% 
    select(names(col_total)[col_total > 0])
  #### FIX WARNING ISSUE HERE#####
  temp <- suppressWarnings(chisq.test(as.matrix(temp_table)))
  mote_temp <- suppressWarnings(v.chi.sq(x2 = temp$statistic, n = sum(temp_table), 
                        r = nrow(temp_table), c = ncol(temp_table), 
                        a = .05))
  small_effect$year[i] <- year
  small_effect$v[i] <- mote_temp$v
  small_effect$low[i] <- mote_temp$vlow
  small_effect$high[i] <- mote_temp$vhigh
  i <- i + 1
}

ggplot(small_effect, aes(year,v)) + 
  geom_point() + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab("Effect Size")

DF_decade <- DF$small_first_gp %>% 
  mutate(who = "First") %>% 
  bind_rows(
    DF$small_other_gp %>% 
      mutate(who = "Other")
  ) %>% 
  mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
  group_by(who, Decade) %>% 
  summarize_all(sum) %>% 
  pivot_longer(cols = `Western Europe`:Mirconesia,
               names_to = "Country", 
               values_to = "Count")

DF_decade$region <- factor(
  DF_decade$Country,
  levels = unique(DF_decade$Country),
  labels = 
)

"Africa"
"Americas"
"Asia"
"Europe"
"Oceania"

ggplot(DF_decade, aes(who, Count, fill = Country)) + 
    geom_bar(position="fill", stat="identity") + 
  theme_classic() + 
  facet_grid(~Decade) + 
  xlab("Author Type") + 
  ylab("Percent")

## do the seven big regions
```
